R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
misc cleanup and addition of some todo items

A subtle difference, but Markdown is more readable because there are not any
letters injected, and it is _much faster_ to type. It also has more simplicity
in its objectives and flexibility in its output, so where HTML is rendered
almost exclusively in browsers, Markdown can be relevant for the web, print, and
even computer terminals.

@@

When creating a new document in the RStudio IDE, you might notice an option
to create a "R Notebook" or "R Markdown Notebook." This is offered in addition
to the long-known "R Markdown," and the differences are subtle.

@@

- templates, formatting, or other output styles
- parameters
- output document type
-

>>>>

A subtle difference, but Markdown is more readable because there are not any
letters injected, and it is _much faster_ to type. It also has more simplicity
in its objectives and flexibility in its output, so where HTML is rendered
almost exclusively in browsers, Markdown can be relevant for the web, print, and
even computer terminals (todo image).

@@

When creating a new document in the RStudio IDE (todo link to figure), you might notice an option
to create a "R Notebook" or "R Markdown Notebook." This is offered in addition
to the long-known "R Markdown," and the differences are subtle.

@@

- templates, formatting, or other output styles
- parameters
- output document type
